%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Resume
%
% License:
% GNU GPL-3.0 (https://opensource.org/licenses/GPL-3.0)
%
% Important notes:
% This template needs to be compiled with XeLaTeX.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[a4paper]{resume}

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

\lastupdated % Print the Last Updated text at the top right

\namesection{Ujjwal}{Arora}{
Greater New York City Area \\
\urlstyle{same}\url{http://ujjwalarora.xyz} \\
\href{mailto:arora.ujjwal@gmail.com}{arora.ujjwal@gmail.com} | +91.701.995.3464
}

%----------------------------------------------------------------------------------------
%	LEFT COLUMN
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page

%------------------------------------------------
% Education
%------------------------------------------------

\section{Education}

\subsection{Manipal Institute of \\ Technology}

\descript{B.Tech. in Information Technology}
\location{Expected May 2018 | Manipal, India \\ CGPA: 9.01 (Scale: 10.0)}

\sectionspace % Some whitespace after the section


%------------------------------------------------
% Links
%------------------------------------------------

\section{Links}

Github:// \href{https://github.com/azwreith}{\bf azwreith} \\
LinkedIn:// \href{https://in.linkedin.com/in/aroraujjwal}{\bf aroraujjwal} \\
Facebook:// \href{https://www.facebook.com/arora.ujjwal}{\bf arora.ujjwal} \\
Twitter:// \href{https://twitter.com/DarthUjj}{\bf @azwreith} \\

\sectionspace % Some whitespace after the section


%------------------------------------------------
% Skills
%------------------------------------------------

\section{Skills}

\descript{Programming}
Java \textbullet{} C/C++ \textbullet{}  JavaScript \\
Angular \textbullet{} NodeJS \textbullet{} JQuery  \textbullet{} R\\
Android \textbullet{} PHP \textbullet{} MongoDB \textbullet{} SQL \\
Unity \textbullet{} Python \textbullet{} Flask \textbullet{} Git \\

\vspace{2mm}

\descript{Other Tools}
AutoCAD \textbullet{} 3dsMax \textbullet{} Photoshop

\sectionspace % Some whitespace after the section

%------------------------------------------------
% Awards
%------------------------------------------------

\section{Awards}

\descript{Academic Excellence Award}
\location{January 2017}
Scored 9.53/10.0 GPA in my 5th semester at Manipal Institute of Technology.

\sectionspace % Some whitespace after the section

%----------------------------------------------------------------------------------------

\end{minipage} % The end of the left column
\hfill
%
%----------------------------------------------------------------------------------------
%	RIGHT COLUMN
%----------------------------------------------------------------------------------------
%
\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page

%------------------------------------------------
% Experience
%------------------------------------------------

\section{Work Experience}

\runsubsection{Google Summer of Code}
\descript{| Student Developer}

\location{May 2017 – Aug 2017 | Remote}
\vspace{\topsep} %
\begin{tightitemize}
\item Worked on developing a replacement calendar and scheduling module for LibreHealthEHR.
\item  This also involved removal of references to legacy modules, isolation of the SMARTY template engine, and writing database migration scripts.
\end{tightitemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{Firexit Software}
\descript{| Unity Game Development Intern}

\location{Sep 2015 – Nov 2015 | Manipal, India}
\begin{tightitemize}
\item Created several modules for the android game {\href{https://play.google.com/store/apps/details?id=com.firexit.speedstreet2VRdemo}{Speed Street 2}}.
\item Successfully designed and developed an arcade game for android in Unity.
\end{tightitemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------
% Projects
%------------------------------------------------

\section{Projects}


\descript{\href{https://github.com/Whos-Up-Team/WhosUp}{Who's Up?!}}

\location{Apr 2017}

\begin{tightitemize}
\item A social app for Android which acts as virtual notice board for strangers to signal when
they’re free for an impromptu meet up or activity (think Tinder, but for events).
\item Originally made for Windows Phone during Microsoft’s code.fun.do Hackathon.
\end{tightitemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------

\descript{\href{https://github.com/azwreith/elementary-browser}{Elementary Browser}}

\location{Nov 2016}

\begin{tightitemize}
\item A light-weight browser I co-built on Electron, with features such as unified search/address bar, history, and bookmarks.
\end{tightitemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------

\descript{\href{https://github.com/azwreith/got-twitter-stream}{got-twitter-stream}}

\location{Jul 2016}

\begin{tightitemize}
\item A real time twitter stream client built using Node and React.
\item Tweets are initially rendered on the server-side; new tweets that come in are emitted via Socket.io.
\end{tightitemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------

\descript{\href{https://github.com/azwreith/cracker-news}{cracker-news}}

\location{Jun 2016}

\begin{tightitemize}
\item A Reddit-like Hacker News clone built on top of the MEAN stack.
\end{tightitemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------


\section{Other Experience}

\descript{{\href{http://librehealth.io}{LibreHealth}} | Contributor}
\location{2016 - Present}
Submitted several patches to LibreEHR addressing vital issues as well as adding new features.

\sectionspace % Some whitespace after the section

\descript{\href{http://www.resolutionproject.org/ventures/teach-code-good}{Teach Code for Good} | Python Instructor}
\location{2016 - 2017}
A student run social venture which aims to empower children from at-risk backgrounds, create interest in coding, and increase opportunities for education and employment.

\sectionspace % Some whitespace after the section

\descript{{\href{http://wearemist.in}{MIST}, Manipal University} | Tech Head (Cryptography)}
\location{2016 - 2017}
Successfully designed and developed the society website in Angular.


\sectionspace % Some whitespace after the section

%----------------------------------------------------------------------------------------

\end{minipage} % The end of the right column

%----------------------------------------------------------------------------------------
%	SECOND PAGE (EXAMPLE)
%----------------------------------------------------------------------------------------

%\newpage % Start a new page

%\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page

%\section{Example Section}

%\end{minipage} % The end of the left column
%\hfill
%\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page

%\section{Example Section 2}

%\end{minipage} % The end of the right column

%----------------------------------------------------------------------------------------

\end{document}
