%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Engineering Intern | Android, iOS, UIAutomator, Robot Framework, Node, Angular5} % Job title
    {Citrix} % Organization
    {Bangalore, India} % Location
    {Jan. 2018 - Jun. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      	\item {Helped improve the reliability of XenMobile BVT and FVT by solving challenges pertaining to application testing and automation.}
      	\item {Created a "mock" app that covered all the third-party interactions with Citrix XenMobile applications which helped reduce effort required for building test cases and made the existing tests more robust. }
        \item {Developed a dashboard application that allowed XenMobile managers, developers, and stakeholders to gauge the status of daily test suite runs.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Student Developer | PHP, JavaScript} % Job title
    {Google Summer of Code} % Organization
    {Remote} % Location
    {May. 2017 - Aug. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked on developing a replacement calendar and scheduling module for LibreHealthEHR.}
        \item {This also involved removal of references to legacy modules, isolation of the SMARTY template engine, and writing database migration scripts.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Unity Game Developer Intern | Unity, C\#} % Job title
    {Firexit Software} % Organization
    {Manipal, India} % Location
    {Sep. 2015 - Nov. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Created several modules for the android game {\href{https://play.google.com/store/apps/details?id=com.firexit.speedstreet2VRdemo}{Speed Street 2}}.}
        \item {Designed and developed an arcade game for android in Unity.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
